Bootstrap Confidence Intervals for Regression Discontinuity Designs with Uniform Kernels

### 2016-02-24 main_paper.tex
This commit adds a paragraph to Intro and the bibliography. Something odd is happening with Van Der Klaauw 2002 cite. I also edited the setup file to include natbib package.

\begin{abstract}\noindent%
  This paper develops a novel bootstrap procedure to obtain robust
  bias-corrected confidence intervals in regression discontinuity designs that
  use the uniform kernel. The procedure uses a residual bootstrap to estimate
  the bias of the RD estimator, which is then removed from the original RD
  estimator. The bias-corrected estimator is then bootstrapped itself to
  generate valid confidence intervals. This procedure is valid for empirically
  relevant bandwidths when the residual bootstraps use a polynomial of higher
  order than used to estimate the treatment effect and can be applied under the
  same conditions as Calonico, Cattaneo and Titiunik's (2014,
  \textit{Econometrica}) analytical correction.
\end{abstract}

@@

The identification of the treatment effect at the threshold is then based on 
comparing treated and untreated units at the cutoff. As a practical matter this 
involves comparing units within a bandwidth just above and just below the 
threshold. That comparison is most commonly done by implementing a local linear
estimator above and below the cutoff within bandwidths chosen to minimize the 
asymptotic mean squared error (AMSE) as proposed by Imbens and Kalyanaraman(2012)
and extended by \cite{calonico2014} (CCT, henceforth).

>>>>

\begin{abstract}\noindent
  This paper develops a novel bootstrap procedure to obtain robust
  bias-corrected confidence intervals in regression discontinuity designs that
  use the uniform kernel. The procedure uses a residual bootstrap to estimate
  the bias of the RD estimator, which is then removed from the original estimator.
 The bias-corrected estimator is then bootstrapped itself to
  generate valid confidence intervals. This procedure is valid for empirically
  relevant bandwidths when the residual bootstraps use a polynomial of higher
  order than used to estimate the treatment effect and can be applied under the
  same conditions as Calonico, Cattaneo and Titiunik's (2014,
  \textit{Econometrica}) analytical correction.
\end{abstract}

@@

The identification of the treatment effect at the threshold is then based on 
comparing treated and untreated units at the cutoff. As a practical matter this 
involves comparing units within a bandwidth just above and just below the 
threshold. That comparison is most commonly done by implementing a local linear
estimator above and below the cutoff within bandwidths chosen to minimize the 
asymptotic mean squared error (AMSE) as proposed by \cite{IK}
and extended by \cite{calonico2014} (CCT, henceforth).

RD designs have been used as a strategy to estimate effects of interest in a large range of topics in several areas. For just a few examples, RD designs are common in education, evaluating the impact of investments in school facilities, class sizes, remedial education, early childhood education, and financial aid effects on student achievement and later outcomes \citep{cellini2010,urquiola2009,jacoblefgren2004,ludwig2007,vdk2002}; in health by analyzing the impact of healthcare provision through Medicare, and neo-natal care on low birth weight children mortality \citep{Card2009,barreca2011saving}; in political science providing evidence regarding incumbency advantage in elections, electoral enfranchising and policy changes associated with the introduction of electronic voting, strategic voting behavior, and local media effects and ad expenditure in presidential elections in the U.S. \citep{lee2008,Caughey2011,erikson2015,Fujiwara2015,Fujiwara2011,keele2014geographic}. Several more examples of the breadth of RD designs are listed by \cite{lee2010}.
